Compilation and Backend-Independent Vectorization for Multi-Party Computation

### 2022-04-28 overleaf/compiler.tex
Move 'Code Generation' paragraph header

% Function preamble
The generated MOTION code begins with the declaration of all variables used in the function, including loop counters.  If a variable is a vectorized array, it is initialized to a correctly-sized array of empty MOTION shares.  Additionally, each plaintext variable and parameter has a shared counterpart declared.  Next, all constant values which are used as part of shared expressions are initialized as a shared input from party 0.  Finally, plaintext parameters are converted used as shared inputs from party 0 to initialize their shared counterparts. (Importantly, as we mention, they are converted only if they are needed as an argument to a shared operation; one can think of it as an upcast from \texttt{plain} to \texttt{share}.)

% Non-vectorized assignments and returns
\paragraph{Code generation:}
Once the function preamble is complete, the MPC Source is translated into C++ one statement at a time. The linear structure of MPC Source enables translation. If there is no vectorization present in a statement, translation to C++ is straightforward: outside of MUX statements and array updates, non-vectorized assignments, expressions, and returns directly translate into their C++ equivalents.  Non-vectorized MUX statements are converted to MOTION's MUX member function on the condition variable.  Array updates are translated into two C++ assignments: one to update the value in the original array and one to assign the new array as shown in Listing~\ref{tab:motion_translation_array_updates}.

>>>>

% Function preamble
\paragraph{Code generation:}
The generated MOTION code begins with the declaration of all variables used in the function, including loop counters.  If a variable is a vectorized array, it is initialized to a correctly-sized array of empty MOTION shares.  Additionally, each plaintext variable and parameter has a shared counterpart declared.  Next, all constant values which are used as part of shared expressions are initialized as a shared input from party 0.  Finally, plaintext parameters are converted used as shared inputs from party 0 to initialize their shared counterparts. (Importantly, as we mention, they are converted only if they are needed as an argument to a shared operation; one can think of it as an upcast from \texttt{plain} to \texttt{share}.)

% Non-vectorized assignments and returns
Once the function preamble is complete, the MPC Source is translated into C++ one statement at a time. The linear structure of MPC Source enables translation. If there is no vectorization present in a statement, translation to C++ is straightforward: outside of MUX statements and array updates, non-vectorized assignments, expressions, and returns directly translate into their C++ equivalents.  Non-vectorized MUX statements are converted to MOTION's MUX member function on the condition variable.  Array updates are translated into two C++ assignments: one to update the value in the original array and one to assign the new array as shown in Listing~\ref{tab:motion_translation_array_updates}.
